New lower bounds for Schur and weak Schur numbers

### 2021-04-07 article/article.tex
local

\subsection{}

\subsection{}

>>>>

\begin{remark}
\(SE_+\) and \(S\) have the same asymptotic growth rate.
\end{remark}

\subsection{Inequaties on SE_+}

The main result on \(SE_+\) follows. It allows us to improve lower bounds on Schur numbers by computing \(SE_+\).

\begin{theorem}
Let \(n, k \in \mathbb{N}^*\), we have \\
\[ S(n+k) \geq SE_+(k+1)S(n) \]
\end{theorem}

Using a SAT solvers, we are able to exhibit adequate Schur partitions, i.e satisfying \(SE_+\) constraint, 
hence providing lower bound on \(SE_+\). We refer to such partition as \textit{templates}. Moreover, when using 
a template in the above formula, it is possible to get an additive constant. We seek templates providing "affine"
inequalities : \(aS(n+k) + b \) where \(a\) is a lower bound for \(SE_+(k+1)\). Further details can be found in the \hyperref[SAT]{SAT section}.
\subsection{}
